\section{Academic Experience}

%\cventry{2013--2017}{PhD in High Energy Physics}{}{Imperial College London}{}{Search for supersymmetry in 13TeV proton-proton collisions with the CMS experiment at the LHC.}%
\cventry{2013--2017}{PhD in High Energy Physics}{}{Imperial College London}{}{}
\vspace{0.1cm}
   \cvitem{}{Search for supersymmetry in 13TeV proton-proton collisions with the CMS experiment at the LHC.}
\vspace{0.1cm}
   \cvitem{}{Held a key role in ensuring the results from the $\alpha_T$~search for supersymmetry were among the first to be shown publicly with  $2.3{fb}^{-1}$ of data at CERN in November 2015
   and with $12.9{fb}^{-1}$ of data at ICHEP16}
\vspace{0.1cm}
   \cvitem{}{ Work includes developing the statistical analysis of the search as well as looking at new variables and strategies to optimise sensitivity to a wide range of models.}
\vspace{0.1cm}
   \cvitem{}{ Worked on development of python framework for analysis. }
\vspace{0.1cm}
   \cvitem{}{ For the CMS collaboration, worked to develop the jet algorithm for the Stage 2 upgrade of the CMS level-one trigger, particularly focusing on novel methods of pile-up subtraction.}
\vspace{0.1cm}
   \cvitem{}{ Undertook trigger shifts for CMS.}
\vspace{0.1cm}
   \cvitem{}{ Additionally work with a phenomenology collaboration (MasterCode) to determine the impact of direct searches at CMS and ATLAS on the allowed parameter space of GUT scale models.}
\vspace{0.1cm}
   \cvitem{}{ Moved to France to be based at CERN.}
\vspace{0.1cm}
   \cvitem{}{ Honarary Research Associate at Bristol University (2015-2017).}
\vspace{0.2cm}

\cventry{Summer 2012}{Undergraduate research opportunities programme (UROP)}{}{Imperial College London}{}{}
\vspace{0.1cm}
\cvitem{}{As part of the MasterCode collaboration, recast searches for supersymmetry at the LHC for use in a scan 
of GUT scale models to determine the impact of these searches on the SUSY parameter space.}
\vspace{0.1cm}
\cvitem{}{ Gained experience with event generation (PYTHIA) as well as fast detector simulation (DELPHES).}
\vspace{0.1cm}
\cvitem{}{ Additionally, studied the decay times of long lived supersymmetric taus as part of a proposal for a new search.}
\vspace{0.1cm}
\cvitem{}{ Both parts of the project form sections of publications in which I am a co-author.}
\vspace{0.2cm}

\cventry{Summer 2011}{DAAD Scholarship}{}{Max-Planck-Institut fur Kernphysik (MPIK), Heidelberg}{}{}
\vspace{0.1cm}
\cvitem{}{Research placement working with the electron beam ion trap (EBIT) group at MPIK}
\vspace{0.1cm}
\cvitem{}{ Assist the EBIT group at MPIK with research into highly charged ions.}
\vspace{0.1cm}
\cvitem{}{ Experience in experimental techniques and data analysis from work on using an EBIT as a Penning trap.}
\vspace{0.1cm}
\cvitem{}{ Hardware experience from operating EBIT as well as designing and producing electrical field setup for Penning trap}

\vspace{0.2cm}

\cventry{Summer 2010}{Work placement}{}{Scottish Universities Environmental Research Centre (SUERC)}{}{}
\vspace{0.1cm}
\cvitem{}{Research placement working with the luminescence department at SUERC}
\vspace{0.1cm}
\cvitem{}{Gained experience in experimental techniques and data analysis 
investigating the luminescent properties of different materials with the aim of using luminescence as an environmental dosimeter.}
