% Publications from a BibTeX file without multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% for BibTeX numerical labels
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{elwood} % 'elwood' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
\section{Scientific communication}
\subsection{Workshops and conferences}
\cvitem{2019} {Physics Beyond Colliders Working Group meeting "Update on milliQan".}
\vspace{0.1cm}
\cvitem{2019} {Gave presentation on the connections between the Higgs and long-lived particles at the Higgs XS Working Group meeting.}
\vspace{0.1cm}
\cvitem{2019} {Presented update on the milliQan experiment at Searching for long-lived particles at the LHC: Fourth workshop of the LHC LLP Community.}
\vspace{0.1cm}
\cvitem{2017} {Presented the simplified likelihood framework at the LHC Dark Matter Working Group public meeting.}
\vspace{0.1cm}
\cvitem{2014 and 2016}{Presented results of all-hadronic SUSY search and trigger work at meeting of all UK institutes working on CMS.}
\vspace{0.1cm}
\cvitem{2016}{Presented results of all-hadronic SUSY search at the joint annual HEPP and APP conference in Brighton.}
\vspace{0.1cm}
\subsection{Seminars}
\cvitem{2019} {The Ohio State University "Searching for Long-lived Particles (Far) Beyond the Tracker".}
\vspace{0.1cm}
\cvitem{2019} {Ecole Polytechnique Federale Lausanne "The milliQan experiment: search for milli-charged particles at the LHC".}
\vspace{0.1cm}
\cvitem{2019} {CERN LPCC Seminar "Searches for disappearing and emerging new particles at CMS".}
\vspace{0.1cm}
\cvitem{2019} {University of California, Santa Barbara "Searches for disappearing and emerging new particles at CMS".}
\vspace{0.1cm}
\cvitem{2018} {Imperial College London "The milliQan experiment: search for milli-charged particles at the LHC".}
\vspace{0.1cm}
\cvitem{2017} {University of California, Santa Barbara "From LHC searches to constraints on GUT-scale SUSY models: the CMS alphaT search for SUSY, reinterpretation and towards the future".}
\vspace{0.1cm}

% \subsection{Summer schools}
% \cvitem{2016}{Attended the CERN-Fermilab Summer School in Fermilab, Chicago}

\subsection{Events organised}
\cvitem{2020}{Part of the organisational committee for Searching for long-lived particles at the LHC: Seventh workshop of the LHC LLP Community.}
\cvitem{2020}{Organised CMS Long-lived particle workshop at CERN with co-convenor of CMS Exotica LLP group at CERN.}
\vspace{0.1cm}
\cvitem{2019}{Organised long-lived session of CMS Exotica workshop in Aachen with co-convenor of CMS Exotica LLP group.}
\vspace{0.1cm}
\cvitem{2018}{Organised milliQan workshop and collaboration meeting at University of California, Santa Barbara.}
\vspace{0.1cm}
\section{Publications}
\cvitem{}{As a member of the CMS Collaboration for several years, I am a
  co-author of more than 570 publications, which can be found at
  \href{http://inspirehep.net/author/profile/M.Citron.2}{\texttt{inSPIRE}}. I have provided significant
  contributions to the following publications, conference proceedings,
  preliminary results, and public notes.}
  % I have been a co-author of five papers as a member of the MasterCode collaboration, three phenomenology papers with other collaborators, and one paper as a member of the milliQan collaboration.}
  \cvlistitem{The search I coordinated for fractionally charged particles with the milliQan prototype is detailed in Reference~\cite{ball2020search}.}
  \cvlistitem{The search I undertook using calorimetry timing within the CMS collaboration is detailed in Reference~\cite{2019134876}.} 
  \cvlistitem{My extensive contributions to the $\alpha_T$~search led to References~\cite{CMS:2016dbr,CMS:2015dbr}.} 
  \cvlistitem{The work I undertook on the reinterpretation of collider searches using the simplified likelihood framework is detailed in References~\cite{simplifiedLikelihood,Buckley_2019}.} 
  \cvlistitem{My work developing the jet and pileup subtraction algorithm for the CMS L1 trigger formed a key part of References~\cite{Zabi:2016ljo,Kreis:2015jjr}.}
  \cvlistitem{My work as part of the MasterCode collaboration, including the reinterpretation of collider searches, forms a key part of References~\cite{Bagnaschi:2016afc,Bagnaschi:2015eha,Buchmueller:2014yva,Buchmueller:2012hv,deVries:2015hva,Buchmueller:2015uqa}.}
  \cvlistitem{The phenomological study of metastable staus, for which I studied the collider signatures, is detailed in Reference~\cite{Citron:2012fg}.}
\bibliographystyle{unsrt}
\bibliography{citron_CV} % 'citron' is the name of a BibTeX file

